---
title: "Statistical Inference Project"
author: "Erik Rehnberg Steeb"
date: "7/23/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

## Overview

## Setup

The first step is to set our initial variables and set the seed so this is fully reproducible.
```{r}
ECHO=TRUE
set.seed(1775)
lambda = 0.2
exp = 40
```

Next we run our simulation with the parameters set above.
```{r, echo=TRUE}
sim_means = NULL
for (i in 1 : 1000) {
  sim_means = c(sim_means, mean(rexp(exp, lambda)))
}
```


## Compare Sample and Theoretical Means

#### Sample Mean

```{r sample mean, echo=TRUE}
mean_sim_means <- mean(sim_means)
mean_sim_means
```

#### Theoretical mean
The theoretical mean of the distribution is lambda ^ -1

```{r theoretical,echo=TRUE}
theo_mean <- lambda^-1
theo_mean
```

#### Comparison
The difference is fairly small.
``` {r comp, echo=TRUE}
abs(mean_sim_means - theo_mean)
```

## Sample Variance and Theoretical Variance
#### Sample Variance
Again, this is very simple
``` {r}
var_sim <- var(sim_means)
```

#### Theoretical Variance
The theoretical variance follows
``` {r}
theo_var  <- (lambda * sqrt(exp))^-2
```

#### Compared variances
Again, a very slight difference between the two
``` {r}
abs(var_sim - theo_var)
```

## Distribution
Next, I'll directly compare a density histogram of the one thousand simulations with the normal distribution, which has a mean of lambda^-1 and std deviation of (lambda*sqrt(n))^-1, which is the theoretical distribution for the simulations. They are fairly similar, with the exception of the peak of the simulation occuring just after the peak of the theoretical mean. 
``` {r}
df <- data.frame(sim_means)

ggplot(df, aes(x = (unlist(df)))) + 
  geom_histogram(aes(y= ..density..), binwidth = 0.2)+
  stat_function(fun = dnorm,
                args = list(mean = lambda^-1, 
                       sd=(lambda*sqrt(exp))^-1),
                size = 2) + 
  labs(title = "Histogram of Simulations", x = "Mean of the Simulation")
```